\providecommand{\main}{../../main}
\documentclass[../../main.tex]{subfiles}


\begin{document}

    \chapter{Abstract}
    
    \label{sec:Abstract}

    The \acrfull{hllhc} will open an unprecedented window on the weak-scale nature of the universe, providing high-precision measurements of the standard model electroweak interaction, including properties of the Higgs Boson, as well as searches for new physics beyond the standard model. The new requirements in terms of rate and latency exceed the present capabilities of the front-end and back-end electronics forcing the entire replacement of the \acrshort{cms} main parts including the trigger system.
    
    The \acrshort{hllhc}, will start operating after the third Long Shutdown (LS3), and is designed to provide an increased instantaneous luminosity, at the price of extreme pileup of interactions. In LS3, the CMS detector will also undergo a major upgrade to prepare for the so called Phase-2 of the \acrshort{lhc} physics program, starting in the second half of 2027.
    
    Aim of this thesis is to contribute to the development of a new \acrfull{l1} trigger for the \acrshort{cms} Experiment, in particular on the new \acrfull{gt} subsystem. The \acrshort{cms} L1 trigger performs the first step of event reduction, based on physics selections. The L1 hardware consists of custom programmable electronics working at local, regional and global scale. Within L1, the Global Trigger (GT, top entity of the hierarchy) is responsible for selecting events to be processed by the following software trigger stage.  
    
    The GT decision is presently based on calculations of physics parameters applied to candidate particles and global parameters. Such algorithms range from setting thresholds on transverse (p, E) on single objects to more complex calculations based on multiplicities and topological conditions.  
    
    The new GT shall consist of multiple processors, each receiving the full set of trigger objects, but calculating different set of algorithms, namely the \textit{trigger menu}. The use of advanced object identification algorithms, including machine learning and multivariate analysis techniques, will facilitate greater use of object classification variables in the GT. 
    
    %The thesis work will be sub-divided in two main branches.
    
    %Firstly a new types of algorithms will be studied in the HL-LHC setup, namely the neural networks based algorithms; to do so, the powerful \textit{hls4ml} tool will be employed to perform the translation from high level programming code (Python and Keras) to \textit{High Level Synthesis} (HLS), finally this code will be employed to produce a bit-file to be loaded on \textit{Field Programmable Gate Arrays} (FPGAs). The algorithms produced will be firstly simulated in software, then tested in a fast way on PYNQ accelerator card and finally implemented in the processor board and the results compared to the expected values.
    
    %Then the Final-OR (finor) board firmware will be developed, this board has the aim to monitor and eventually pre-scale the incoming 1000 different algorithms, then merging them and produce up to 8 different trigger types. These trigger types are chosen according to the physics program needed.  
    %The code currently implemented in the present Global Trigger board, developed by the Vienna CMS group, will be revisited and modified to match the updated features of the Phase-2 upgrade. Firstly the firmware must be revisited, since in the Final-OR logic will be deployed in an upgraded version of the current used FPGA (Virtex-7 $\to$ Virtex-Ultrascale$+$). 
    %Secondly, new feature will be added to meet the new requirements of the Phase-2 upgrade in therms of increased trigger rate, number of algorithms and input data throughput. 
    
    %Lastly the interface to the Timing and Control Distribution System (TCDS-2) must be developed and implemented in the finor board to distribute the trigger signals (multiple trigger Physics) to the detector readout electronics.
    

\end{document}