%\providecommand{\main}{../../main}
%\documentclass[../../main.tex]{subfiles}


\begin{thebibliography}{99}

%\renewcommand{\baselinestretch}{1} 
%\small

\bibitem{LHC}
\textit{LHC: Large Hadron Collider}
\\\url{https://home.cern/science/accelerators/large-hadron-collider}

\bibitem{LHC-Acc}
\textit{LHC: Accelerator complex}
\\\url{https://home.cern/science/accelerators/accelerator-complex}

\bibitem{CMS}
\textit{CMS detector}
\\\url{https://cms.cern/detector}

\bibitem{Si-track}
V Karimäki et al.
\textit{The CMS tracker system project: Technical Design Report,}
Geneva: CERN, 1997.

\bibitem{Si-track-up}
CMS Collaboration.
\textit{The Phase-2 Upgrade of the CMS Tracker,}
Tech. rep. CERN-LHCC-2017-009. CMS-TDR-014. \\
Geneva: CERN, 2017. 

\bibitem{ECAL}
\textit{The CMS electromagnetic calorimeter project: Technical Design Report,}
Geneva: CERN, 1997.

\bibitem{HCAL}
\textit{The CMS hadron calorimeter project: Technical Design Report,}
Geneva: CERN, 1997.

\bibitem{HGCAL}
CMS Collaboration.
\textit{The Phase-2 Upgrade of the CMS Endcap Calorimeter,}
Tech. rep. CERN-LHCC-2017-023. CMS-TDR-019. \\
Geneva: CERN, 2017. 

\bibitem{Muon-cham}
\textit{The CMS muon project: Technical Design Report,}
Technical Design Report CMS. \\
Geneva: CERN, 1997.

\bibitem{Muon-up}
CMS Collaboration.
\textit{The Phase-2 Upgrade of the CMS Muon Detectors,}
Tech. rep. CERN-LHCC-2017-012. CMS-TDR-016. \\
Geneva: CERN, 2017. 

\bibitem{L1T}
Sergio Cittolin, Attila Rácz, and Paris Sphicas.
\textit{CMS The TriDAS Project: Technical Design Report, Volume 2: Data Acquisition and
High-Level Trigger. CMS trigger and data-acquisition project,}
Geneva: CERN, 2002.

\bibitem{L1T-1up}
A Tapper and Darin Acosta.
\texit{CMS Technical Design Report for the Level-1 Trigger Upgrade,}
Tech. rep. CERN-LHCC-2013-011. CMS-TDR-12. \\
Geneva: CERN, 2013.

\bibitem{Muon_kalman}
M. Bachtis et al.
\texit{"Upgrade of the CMS Barrel Muon Track Finder for HL-LHC featuring a Kalman Filter algorithm and an ATCA Host Processor with Ultrascale+ FPGAs",}
In: PoS TWEPP2018 (2019), p. 139. \\
DOI: 10.22323/1.343.0139 .
\bibitem{TMUX}
R. Frazier et al.
\textit{"A demonstration of a time multiplexed trigger for the CMS experiment",}
In: JINST 7 (2012), p. C01060.
DOI: 10.1088/1748-0221/7/01/C01060 .

\bibitem{uGT}
\textit{Global Trigger firmware Specification for MP7 platform for Upgrade Phase I}
\\\url{https://github.com/cms-l1-globaltrigger/mp7_ugt_legacy/blob/master/doc/mp7_ugt_firmware_specification/pdf/gt-mp7-firmware-specification.pdf}

\bibitem{L1T-2up}
CMS Collaboration.
\texit{The Phase-2 Upgrade of the CMS Level-1 Trigger,}
Technical Design Report. \\
Tech. rep. CERN-LHCC-2020-004. CMS-TDR-21. \\
Geneva: CERN, 2020.

\bibitem{PUPPI}
Daniele Bertolini et al.
\texit{“Pileup Per Particle Identification”,}
In: JHEP 10.arXiv:1407.6013 (2014), 59. 23 p. \\
DOI : 10.1007/JHEP10(2014)059 .

\bibitem{TCDS2}
CMS Collaboration.
\texit{“The Phase-2 Upgrade of the CMS DAQ Interim Technical Design
Report”,}
Tech. Rep. CERN-LHCC-2017-014. CMS-TDR-018. \\
Geneva: CERN, 2017.

\bibitem{Serenity}
Andrew Rose et al.
\texit{“Serenity: An ATCA prototyping platform for CMS Phase-2”,}
DOI: 10.22323/1.343.0115.

\bibitem{perceptron}
\textit{The perceptron: a probabilistic model for information storage and organization in the brain}
\\\url{http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.335.3398}

\bibitem{relu}
\textit{Deep Learning using Rectified Linear Units (ReLU)}
\\\url{https://arxiv.org/pdf/1803.08375.pdf}

\bibitem{elu}
\textit{Fast and Accurate Deep Network Learning by Exponential Linear Units (ELUs)}
\\\url{https://arxiv.org/abs/1511.07289}

\bibitem{gelu}
\textit{Gaussian Error Linear Units (GELUS)}
\\\url{https://arxiv.org/pdf/1606.08415.pdf}

\bibitem{bert}
\textit{BERT: Pre-training of Deep Bidirectional Transformers for
Language Understanding}
\\\url{https://arxiv.org/pdf/1810.04805.pdf}

\bibitem{gpt}
\textit{Language Models are Unsupervised Multitask Learners}
\\\url{https://cdn.openai.com/better-language-models/language_models_are_unsupervised_multitask_learners.pdf}

\bibitem{lossfunc}
\textit{On Loss Functions for Deep Neural Networks
in Classification}
\\\url{https://arxiv.org/pdf/1702.05659.pdf}

\bibitem{kullbackeff}
\textit{Optimism in Reinforcement Learning and Kullback-Leibler Divergence
}
\\\url{https://arxiv.org/abs/1004.5229}

\bibitem{kullbackeff2}
\textit{Why Deep Learning Methods Use KL Divergence
Instead of Least Squares: A Possible Pedagogical
Explanation}
\\\url{https://scholarworks.utep.edu/cgi/viewcontent.cgi?article=2188&context=cs_techrep}

\bibitem{adam}
\textit{Adam: A Method for Stochastic Optimization}
\\\url{https://arxiv.org/abs/1412.6980}

\bibitem{FPGA-inf}
Xilinx-AMD.
\texit{“Accelerating DNNs with Xilinx Alveo Accelerator Cards”,}
WP504 (v1.0.1) October 14, 2018.

\bibitem{hls4ml-DNN}
Javier Duarte et al.
\texit{“Fast inference of deep neural networks in FPGAs for particle physics”,}
J. Instrum. 13 (2018),
no. 07, P07027, doi:10.1088/1748-0221/13/07/P07027, arXiv:1804.06913.

\bibitem{hls4ml-CNN}
Thea Aarrestad et al.
\texit{“Fast convolutional neural networks on FPGA with hls4ml”,}
2021 Mach. Learn.: Sci. Technol. 2 045015,
DOI: 10.1088/2632-2153/ac0ea1

\bibitem{Xilinx-GT}
Xilinx-AMD.
\texit{“Leveraging UltraScale Architecture Transceivers for High-Speed Serial I/O Connectivity”,}
WP458 (v2.0) October 29, 2015.

\bibitem{qkeras}
\textit{Ultra Low-latency, Low-area Inference Accelerators using Heterogeneous Deep Quantization with QKeras and hls4ml}
\\\url{https://doi.org/10.48550/arXiv.2006.10159}

\bibitem{tfmot}
\textit{Tensorflow Model Optimization}
\\\url{https://www.tensorflow.org/model_optimization}

\bibitem{ALVEO-NN}
X. Yu et al.
\texit{"A Data-Center FPGA Acceleration Platform for Convolutional Neural Networks",}
2019 29th International Conference on Field Programmable Logic and Applications (FPL), 2019, pp. 151-158, \\
doi: 10.1109/FPL.2019.00032.

\bibitem{Ihor_thesis}
Ihor Komarov
\texit{Development of neural-network based topological Level-1 triggers for the CMS experiment at the HL-LHC,}
Hamburg: Universität Hamburg, 2022.

\bibitem{DSP_ch}
Xilinx-AMD.
\texit{“Virtex UltraScale+ FPGA Data Sheet: DC and AC Switching Characteristics”,}
DS923 (v1.19) June 23, 2021

\bibitem{EMP}
\textit{EMP Framework}
\\\url{https://serenity.web.cern.ch/serenity/emp-fwk/}

\bibitem{IPbus}
C. Ghabrous Larrea, K. Harder, D. Newbold, D. Sankey, A. Rose, A. Thea and T. Williams,
\textit{"IPbus: a flexible Ethernet-based control system for xTCA hardware",}
JINST 10 (2015) no.02, C02019. DOI: 10.1088/1748-0221/10/02/C02019

\bibitem{Git}
\textit{Final OR GitHub Repository}
\\\url{https://github.com/Gabriele-bot/CMS-FinOR-GT_monitoring}

\end{thebibliography}

%\printbibliography